Language-Based Low-Level MPC Security: $\metaprot$ to $\minifed$

### 2024-05-05 ppdp24/model.tex
checkpoint

In the malicious model we assume that corrupt clients are in the thrall of an
adversary $\adversary$ who does not necessarily follow the rules of the protocol.
We model this by positing a $\arewrite$ function which is given a corrupt memory
$\store_C$ and expression $\be$, and returns a rewritten expression that can
be interpreted to yield a corrupt input. Then we define an evaluation
relation that incorporates the adversary.

>>>>

In the malicious model we assume that corrupt clients are in the
thrall of an adversary $\adversary$ who does not necessarily follow
the rules of the protocol.  We model this by positing a $\arewrite$
function which is given a corrupt memory $\store_C$ and expression
$\be$, and returns a rewritten expression that can be interpreted to
yield a corrupt input. We define the evaluation relation that
incorporates the adversary in Figure \ref{fig-adversary}.

Another important distinction of the malicious setting is that it
typically incorporates \emph{abort}. Honest parties implement
strategies to detect rule-breaking-- aka \emph{cheating}-- by
using, e.g., message authentication codes with semi-homomorphic
properties as in BDOZ and SPDZ \cite{XXX}. If cheating is
detected, the protocol is aborted. To model this, we extend
$\minifed$ with abort $\bot$ and an \emph{assert} command.
\begin{definition}
  We add $\bot$ to our syntax of programs and add the form
  $\elab{\assert(\phi(\be))}{\cid}$ to the command syntax of $\minifed$,
  with semantics given in Figure \ref{fig-adversary}. We also extend the
  domain of memories $\store$ to $\mathbb{F}_p \cup \{ \bot \}$.
\end{definition}
